Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-14 paper/sheaf_lics.tex
explicit section on modalities

\newcommand{\IsType}[1]{\mathrm{Is\mymathhyphen}#1\mathrm{\mymathhyphen
    type}}
\newcommand{\modal}{\ensuremath{\ocircle}}
\newcommand \True {\mathrm{true}}
\newcommand \False {\mathrm{false}}
\newcommand \closure[1] {\overline{#1}}
\newcommand \Char[1] {\chi_{#1}}%{\mathrm{char}(#1)}
\newcommand \E {\mathcal{E}}
\newcommand \Hom[1] {\mathrm{Hom}_{#1}}
\newcommand \Sh[1] {\mathrm{Sh}_{#1}}

@@

A left exact modality leads to a new theory with new principles.

@@

>>>>

\newcommand{\IsType}[1]{\mathop{\mathrm{Is\mymathhyphen}#1\mathrm{\mymathhyphen
      type}} }
\newcommand{\modal}{\ensuremath{\ocircle}}
\newcommand \True {\mathrm{true}}
\newcommand \False {\mathrm{false}}
\newcommand \closure[1] {\overline{#1}}
\newcommand \Char[1] {\chi_{#1}}%{\mathrm{char}(#1)}
\newcommand \E {\mathcal{E}}
\newcommand \Hom[1] {\mathrm{Hom}_{#1}}
\newcommand \Sh[1] {\mathrm{Sh}_{#1}}

@@

A left exact modality leads to a new homotopy type theory with
potentially new principles.

Definition of Sigma-Types.

Preservation of univalence.

Consistency issues.

@@

Talk about issues in universe levels. Lake of cumulativity for
$\Type_n$ and impossibility to define by induction the sheafification 
because universe levels must be the same for every $n$.
